\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-10-18 paper/ms.tex
Updated a number
semicolons in itemize lists

\begin{enumerate}
\item Generate $a \sim$ Normal$(0, 1)$
\item Generate $b \sim$ Uniform$(0, 1)$
\item Define $t := a/\sqrt{-\ln(b)}$
\item Generate $n \sim$ Normal$(0, 1)$
\item Set $x := 10^{1.5 - 3|t|}n$
\end{enumerate}
The variable $t$ has a student-$t$ distribution with 2 degrees of freedom.
Overall, this procedure generates values $x$
with a maximum scale of tens--hundreds, down to
a minimum scale of about $10^{-30}$ with 99\% probability, by virtue
of the $t$-distribution's heavy tails.
For convenience, the \code{RNG} class contains a member function \code{randh()}
to generate values from this distribution.
The factor of \code{1E3} is included because it is a measure of the prior
width. Therefore, this proposal will attempt moves whose maximum order of
magnitude is a bit wider than the prior (since it would be very surprising
if any bigger moves were needed), and will propose moves a few orders of
magnitude smaller with moderate probability. We recommend using
this strategy (a measure of prior width, multiplied by \code{randh()}) as
a default proposal that works well in almost all problems.

@@

\subsection{Mixture model results}
The data and the posterior mean fit are shown
in Figure~\ref{fig:galaxies} and the posterior distribution for
$N$ is shown in Figure~\ref{fig:galaxies_N}.
The marginal likelihood was $\ln(Z) = -242.2$, and
the information (measured in nats) was $\mathcal{H} = 32.3$.

@@

The main challenges associated with ABC are:
\begin{enumerate}[(i)]
\item The choice of discrepancy function $\rho(D; D_{\rm observed})$, which
may involve a choice of summary statistics,
\item How to choose the value of $\epsilon$, or how to change it as a run
progresses,
\item How to make algorithms more efficient than rejection sampling.
\end{enumerate}
Challenge (i) is Bayesian in nature, i.e., it relates to the very
definition of the posterior distribution itself.
On the other hand, challenges (ii) and (iii) are about the computational
implementation. Most ABC analyses are done using Sequential Monte Carlo
\citep[SMC; ][]{del2012adaptive}, another family of algorithms closely related
to Nested Sampling and annealing in the sense that they work with
sequences of probability distributions.

>>>>

\begin{enumerate}
\item Generate $a \sim$ Normal$(0, 1)$;
\item Generate $b \sim$ Uniform$(0, 1)$;
\item Define $t := a/\sqrt{-\ln(b)}$;
\item Generate $n \sim$ Normal$(0, 1)$;
\item Set $x := 10^{1.5 - 3|t|}n$
\end{enumerate}
The variable $t$ has a student-$t$ distribution with 2 degrees of freedom.
Overall, this procedure generates values $x$
with a maximum scale of tens--hundreds, down to
a minimum scale of about $10^{-30}$ with 99\% probability, by virtue
of the $t$-distribution's heavy tails.
For convenience, the \code{RNG} class contains a member function \code{randh()}
to generate values from this distribution.
The factor of \code{1E3} is included because it is a measure of the prior
width. Therefore, this proposal will attempt moves whose maximum order of
magnitude is a bit wider than the prior (since it would be very surprising
if any bigger moves were needed), and will propose moves a few orders of
magnitude smaller with moderate probability. We recommend using
this strategy (a measure of prior width, multiplied by \code{randh()}) as
a default proposal that works well in almost all problems.

@@

\subsection{Mixture model results}
The data and the posterior mean fit are shown
in Figure~\ref{fig:galaxies} and the posterior distribution for
$N$ is shown in Figure~\ref{fig:galaxies_N}.
The marginal likelihood was $\ln(Z) = -241.7$, and
the information (measured in nats) was $\mathcal{H} = 32.0$.

@@

The main challenges associated with ABC are:
\begin{enumerate}[(i)]
\item The choice of discrepancy function $\rho(D; D_{\rm observed})$, which
may involve a choice of summary statistics;
\item How to choose the value of $\epsilon$, or how to change it as a run
progresses; and
\item How to make algorithms more efficient than rejection sampling.
\end{enumerate}
Challenge (i) is Bayesian in nature, i.e., it relates to the very
definition of the posterior distribution itself.
On the other hand, challenges (ii) and (iii) are about the computational
implementation. Most ABC analyses are done using Sequential Monte Carlo
\citep[SMC; ][]{del2012adaptive}, another family of algorithms closely related
to Nested Sampling and annealing in the sense that they work with
sequences of probability distributions.
